Fit by design: Developing substrate-specific seed mixtures for functional dike grasslands

### 2023-03-06 manuscript.Rmd
Update manuscript.Rmd

The aim of this study is to identify the best combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes. An experiment was set up to test agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types. We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deep substrates. Furthermore for slopes, higher seed densities are recommended for a succesfull establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.

>>>>

The aim of this study is to identify the best combinations of seed mixtures and substrates for vital and species-rich grasslands on north- and south-exposed dike slopes. An experiment was set up to test agricultural soil with different amounts of sand admixture, substrate depths, seed densities, and seed mixture types. We expected a better development of dry grassland in the south exposition with shallow and sandy substrates, and of mesic meadows in north exposition on less sandy and deep substrates. Furthermore for slopes, higher seed densities are recommended for a successful establishment [@KleberLerchbaumer.2017], albeit without experimental evidence.
